Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-08-17 paper.tex
Added to paper parts.

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying, 
\[
R e^{j\Phi} = 1 + X.
\]
The joint distribution of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{\sqrt{r^2 - 2r\cos\phi + 1}}.
\]
The mean of $R e^{j\Phi}$ is equal to one because the mean of $X$ is zero.  So,
\begin{equation}\label{eq:expectRepartRphi}
\expect \Re(R e^{j\Phi}) = \expect R \cos(\Phi) = 1,
\end{equation}
where $\Re(\cdot)$ denotes the real part, and
\begin{equation}\label{eq:expectImpartRphi}
\expect \Im(R e^{j\Phi}) = \expect R \sin(\Phi) = 0,
\end{equation}
where $\Im(\cdot)$ denotes the imaginary part.  %The next lemma will be useful for the analysis of the least squares estimator.

\begin{lemma}\label{lem:gg2cont}
Let $X = Z e^{j\Theta}$ be a circularly symmetric complex random variable with pdf $\tfrac{1}{2\pi}f_Z(z)$.  Let $R > 0$ and $\Phi \in [0, 2\pi)$ be random variables satisfying $R e^{j\Phi} = 1 + X$ and with pdf $f(r,\phi)$.  Let
\[
g(\phi) = \int_{0}^\infty r f(r, \phi) dr,
\]
and
\[
g_2(\phi) = \int_{0}^\infty r^2 f(r, \phi) dr.
\]
Then $g$ and $g_2$ are continuous functions from $\reals$ to $\reals$.
\end{lemma}
\begin{IEEEproof}
BLERG
\end{IEEEproof}

>>>>

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying, 
\[
R e^{j\Phi} = 1 + X.
\]
The joint pdf of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{2\pi\sqrt{r^2 - 2r\cos\phi + 1}}.
\]
The mean of $R e^{j\Phi}$ is equal to one because the mean of $X$ is zero.  So,
\begin{equation}\label{eq:expectRepartRphi}
\expect \Re(R e^{j\Phi}) = \expect R \cos(\Phi) = 1,
\end{equation}
where $\Re(\cdot)$ denotes the real part, and
\begin{equation}\label{eq:expectImpartRphi}
\expect \Im(R e^{j\Phi}) = \expect R \sin(\Phi) = 0,
\end{equation}
where $\Im(\cdot)$ denotes the imaginary part.  %The next lemma will be useful for the analysis of the least squares estimator.

\begin{lemma}\label{lem:gg2cont}
Let $X = Z e^{j\Theta}$ be a circularly symmetric complex random variable with continuous pdf $\tfrac{1}{2\pi}f_Z(z)$.  Let $R > 0$ and $\Phi \in [0, 2\pi)$ be random variables satisfying $R e^{j\Phi} = 1 + X$ and with joint pdf $f(r,\phi)$.  Then
\[
g(\phi) = \int_{0}^\infty r f(r, \phi) dr,
\]
and
\[
g_2(\phi) = \int_{0}^\infty r^2 f(r, \phi) dr.
\]
are continuous functions from $\reals$ to $\reals$.
\end{lemma}
\begin{IEEEproof}
We only give a proof for $g_2$, the proof for $g$ being similar.  From 
\end{IEEEproof}

### 2012-08-17 paper1.tex
Added to paper parts.

Before describing the statistical properties of the least squares estimator, we first require some properties of complex valued random variables.  A complex random variable $X$ is said to be \emph{circularly symmetric} if the distribution of its phase $\angle{X}$ is uniform on $[0,2\pi)$ and is independent of the distribution of its magnitude $\abs{X}$.  That is, if $Z \geq 0$ and $\Theta \in [0,2\pi)$ are real random variables such that $Ze^{j\Theta} = X$, then $\Theta$ is uniformly distributed on $[0,2\pi)$ and is indepedent of $Z$.  If the probability density function (pdf) of $Z$ is $f_Z(z)$, then the joint pdf of $\Theta$ and $Z$ is 
\[
f_{Z,\Theta}(z,\theta) = \frac{1}{2\pi}f_Z(z).
\]  
Observe that for any real number $\phi$, the distribution of $X$ and $e^{j\phi}X$ are the same, that is, the distribution is invariant to phase rotation.  If $\expect\abs{X} = \expect Z$ is finite, then $X$ has zero mean because
\begin{align*}
\expect X &= \int_{0}^{2\pi} \int_{0}^\infty z e^{j\theta} f_{Z,\Theta}(z,\theta) dz d\theta \\
&= \frac{1}{2\pi} \int_{0}^{2\pi} e^{j\theta} \int_{0}^\infty z f_Z(z) dz d\theta \\
&= \frac{1}{2\pi}\expect Z \int_{0}^{2\pi} e^{j\theta} d\theta = 0.
\end{align*}

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying, 
\[
R e^{j\Phi} = 1 + X.
\]
The joint distribution of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{\sqrt{r^2 - 2r\cos\phi + 1}}.
\]
The mean of $R e^{j\Phi}$ is equal to one because the mean of $X$ is zero.  So,
\begin{equation}\label{eq:expectRepartRphi}
\expect \Re(R e^{j\Phi}) = \expect R \cos(\Phi) = 1,
\end{equation}
where $\Re(\cdot)$ denotes the real part, and
\begin{equation}\label{eq:expectImpartRphi}
\expect \Im(R e^{j\Phi}) = \expect R \sin(\Phi) = 0,
\end{equation}
where $\Im(\cdot)$ denotes the imaginary part.  %The next lemma will be useful for the analysis of the least squares estimator.

\begin{lemma}\label{lem:gg2cont}
Let $X = Z e^{j\Theta}$ be a circularly symmetric complex random variable with pdf $\tfrac{1}{2\pi}f_Z(z)$.  Let $R > 0$ and $\Phi \in [0, 2\pi)$ be random variables satisfying $R e^{j\Phi} = 1 + X$ and with joint pdf $f(r,\phi)$.  Then
\[
g(\phi) = \int_{0}^\infty r f(r, \phi) dr,
\]
and
\[
g_2(\phi) = \int_{0}^\infty r^2 f(r, \phi) dr.
\]
are continuous functions from $\reals$ to $\reals$.
\end{lemma}
\begin{IEEEproof}
BLERG
\end{IEEEproof}

@@

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\hat{\lambda}_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $\hat{m}_L = \hat{\rho} - \rho_0 G(0)$. %If $g(\phi)$ is continuous at $\phi = \tfrac{2\pi}{M}k+\tfrac{\pi}{M}$ for each $k = 0, 1, \dots M-1$, then 
Then the distribution of $(\sqrt{L}\hat{\lambda}_L, \sqrt{L}\hat{m}_L)$ converges to the bivariate normal with zero mean and covariance
\[
\left( \begin{array}{cc} 
\frac{pA_1 + dA_2}{(p + H d)^2} & 0 \\
0 & \rho_0^2(pB_1 + dB_2)
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = h_2(0) -  2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M}),
\]
\[
A_1 = \var\big( R_1^2\sin^2(\Phi_1) \big), \qquad A_2 = \var\big( R_1^2\sin^2\fracpart{\Phi_1} \big),
\]
\[
B_1 = \var\big( R_1^2 \cos^2(\Phi_1) \big), \;\;\; B_2 = \var\big( R_1^2 \cos^2\fracpart{\Phi_1} \big).
\]
\end{theorem}

\begin{corollary}\label{cor:ampmse}
The mean square error of the amplitude estimator $\hat{\rho}$ is 
\[
\expect (\rho_0 - \hat{\rho})^2 = \rho_0^2\frac{p B_1 + d B_2}{L} + \rho_0^2(1 - G(0))^2 + o(L^{-1/2}).
\] 
\end{corollary}
\begin{IEEEproof} Write
\begin{align*}
\expect (\rho_0 - \hat{\rho})^2 &= \expect \big( \rho_0(1 - G(0)) + G(0)\rho_0 - \hat{\rho} \big)^2 \\
&= \expect \big( \rho_0(1 - G(0)) - \hat{m}_L \big)^2 \\
&= \rho_0^2(1 - G(0))^2 + \expect \hat{m}_L^2 - 2\rho_0(1 - G(0))\expect\hat{m}_L.
\end{align*} 
From Theorem~\ref{thm:normality} it follows that $\expect \hat{m}_L^2 = \tfrac{B}{L} + o(L^{-1})$ and that $\expect \hat{m}_L = o(L^{-1/2})$. 
\end{IEEEproof}

@@

A key assumption in Theorem~\ref{thm:consistency} is that $\abs{G(x)}$ is uniquely maximised at $x = 0$ for $x \in [-\pi, \pi)$.  This assumption asserts that $\abs{G(x)} \leq \abs{G(0)}$ for all $x \in [-\pi, \pi)$ and that if $\{x_i\}$ is a sequence such that $\abs{G(x_i)} \rightarrow \sabs{G(0)}$ as $i \rightarrow \infty$ then $x_i \rightarrow 0$ as $i \rightarrow \infty$.  Although we will not prove it here, this assumption is not only sufficient, but also nescessary, for if $\abs{G(x)}$ is uniquely maximised at some point $x \neq 0$ then $\sfracpart{\theta_0 - \hat{\theta}}_\pi \rightarrow x$ almost surely as $L\rightarrow\infty$, while if $\abs{G(x)}$ is not uniquely maximised then $\sfracpart{\theta_0 - \hat{\theta}}_\pi$ will not converge.  The next Lemma describes a class of circularly symmetric distributions for which $\abs{G(x)}$ is uniquely maximised at $x = 0$.

\begin{lemma}
Let $X = Z e^{j\Theta}$ be a circularly symmetric complex random variable with pdf $\tfrac{1}{2\pi}f_Z(z)$ such that $z^{-1} f_Z(z)$ is nonincreasing with $z$.  Let $R > 0$ and $\Phi \in [0, 2\pi)$ be random variables satisfying $R e^{j\Phi} = 1 + X$.  Let,
\[
h_1(x) = \expect R \cos(x + \Phi) \;\;\; \text{and} \;\;\; h_2(x) =  \expect R \cos\sfracpart{ x + \Phi}.
\]
Then $\abs{h_1(x)}$ is uniquely maximised at $x=0$ over the interval $[-\pi,\pi]$ and $\abs{h_2(x)}$ is uniquely maximised at $x = 0$ over the interval $[-\tfrac{\pi}{M},\tfrac{\pi}{M}]$.
\end{lemma}
Before giving the proof we discuss the requirements of this lemma.  The requirement that $z^{-1}f_{Z}(z)$ be non increasing implies that the pdf of $X$ decreases as we move away from the origin. That is, the pdf of $X$ in rectangular coordinates is $p(x,y) = z^{-1}f_{Z}(z)$, where $z = \sqrt{x^2 + y^2}$, and this is required to be non increasing with $z$.  For example, the zero mean complex Gaussian distribution with independent real and imaginary parts satisfies this requirement.
\begin{IEEEproof}
BLERG
\end{IEEEproof}

@@

Let the noise sequence $\{w_i\}$ be complex Gaussian with independent real and imaginary parts having zero mean and variance $\sigma^2$.  The joint density function of the real and imaginary parts is then
\[
p(x,y) = \frac{1}{2\pi\sigma^2}e^{-(x^2 + y^2)/\sigma^2}
\]
Theorem~\ref{thm:consistency}~and~\ref{thm:normality} hold and, since the distribution of $w_1$ is circularly symetric, the distribution of $R_1e^{j\Phi_1}$ is identical to the distribution of $1 + \frac{1}{\rho_0} w_1$.
%and the joint density function of the real and imaginary parts of $Z$ is
%\[
%p_Z(x,y) = \rho_0^2 p( \rho_0 (x - 1), \rho_0 y ) = \frac{\kappa^2}{2\pi}e^{-\kappa^2(x ^2 - 2x + 1 + y^2) }
%\] 
%where $\kappa = \tfrac{\rho_0}{\sigma}$.  
It can be shown that
\[
g(\phi) = \frac{\cos^2(\phi)}{4\sqrt{\pi}}\left( \frac{e^{-\kappa^2} }{\sqrt{\pi}} + \kappa \Psi(\phi)  e^{-\kappa^2\sin^2(\phi)}\cos(\phi) \right)
\]
where $\kappa = \rho_0/\sigma$ and
\[
\Psi(\phi) = 1 + \erf(\kappa \cos(\phi)) = 1 + \frac{2}{\sqrt{\pi}}\int_0^{\kappa \cos(\phi)} e^{-t^2} dt .
\]
The value of $A_1$ and $A_2$ can be computed by numerical integration.

>>>>

Before describing the statistical properties of the least squares estimator, we first require some properties of complex valued random variables.  A complex random variable $W$ is said to be \emph{circularly symmetric} if the distribution of its phase $\angle{W}$ is uniform on $[0,2\pi)$ and is independent of the distribution of its magnitude $\abs{W}$.  That is, if $Z \geq 0$ and $\Theta \in [0,2\pi)$ are real random variables such that $Ze^{j\Theta} = W$, then $\Theta$ is uniformly distributed on $[0,2\pi)$ and is indepedent of $Z$.  If the probability density function (pdf) of $Z$ is $f_Z(z)$, then the joint pdf of $\Theta$ and $Z$ is 
\[
f_{Z,\Theta}(z,\theta) = \frac{1}{2\pi}f_Z(z).
\]
If $X$ and $Y$ are real random variables equal to the real and imaginary parts of $W = X + jY$ then the joint pdf of $X$ and $Y$ is
\[
f_{X,Y}(x,y) = \frac{f_Z(z)}{2\pi z} \qquad \text{where $z = \sqrt{x^2 + y^2}$.}
\]
Observe that for any real number $\phi$, the pdf of $W$ and $e^{j\phi}W$ are the same, that is, the pdf is invariant to phase rotation.  If $\expect\abs{W} = \expect Z$ is finite, then $W$ has zero mean because
\begin{align*}
 \expect W &= \int_{0}^{2\pi} \int_{0}^\infty z e^{j\theta} f_{Z,\Theta}(z,\theta) dz d\theta \\
 &= \frac{1}{2\pi} \int_{0}^{2\pi} e^{j\theta} \int_{0}^\infty z f_Z(z) dz d\theta \\
 &= \frac{1}{2\pi}\expect Z \int_{0}^{2\pi} e^{j\theta} d\theta = 0.
 \end{align*}

We will have particular use of complex random variables of the form $1 + W$ where $W$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying, 
\[
R e^{j\Phi} = 1 + W.
\]
The joint pdf of $R$ and $\Phi$ can be shown to be
\begin{equation}\label{eq:pdfRPhi}
f(r,\phi) = \frac{r f_Z(\sqrt{\abs{r^2 - 2r\cos\phi + 1}})}{2\pi\sqrt{\abs{r^2 - 2r\cos\phi + 1}}}.
\end{equation}
The mean of $R e^{j\Phi}$ is equal to one because the mean of $W$ is zero.  So,
\begin{equation}\label{eq:expectRepartRphi}
\expect \Re(R e^{j\Phi}) = \expect R \cos(\Phi) = 1,
\end{equation}
where $\Re(\cdot)$ denotes the real part, and
\begin{equation}\label{eq:expectImpartRphi}
\expect \Im(R e^{j\Phi}) = \expect R \sin(\Phi) = 0,
\end{equation}
where $\Im(\cdot)$ denotes the imaginary part.

@@

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\hat{\lambda}_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $\hat{m}_L = \hat{\rho} - \rho_0 G(0)$. %If $g(\phi)$ is continuous at $\phi = \tfrac{2\pi}{M}k+\tfrac{\pi}{M}$ for each $k = 0, 1, \dots M-1$, then 
Then the distribution of $(\sqrt{L}\hat{\lambda}_L, \sqrt{L}\hat{m}_L)$ converges to the bivariate normal with zero mean and covariance
\[
\left( \begin{array}{cc} 
\frac{pA_1 + dA_2}{(p + H d)^2} & 0 \\
0 & \rho_0^2(pB_1 + dB_2)
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = h_2(0) -  2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M}),
\]
\[
A_1 = \expect R_1^2\sin^2(\Phi_1), \qquad A_2 = \expect R_1^2\sin^2\fracpart{\Phi_1},
\]
\[
B_1 = \expect R_1^2 \cos^2(\Phi_1) - 1, \;\;\; B_2 = \expect R_1^2 \cos^2\fracpart{\Phi_1} - h_2^2(0).
\]
\end{theorem}

% \begin{corollary}\label{cor:ampmse}
% The mean square error of the amplitude estimator $\hat{\rho}$ is 
% \[
% \expect (\rho_0 - \hat{\rho})^2 = \rho_0^2\frac{p B_1 + d B_2}{L} + \rho_0^2(1 - G(0))^2 + o(L^{-1/2}).
% \] 
% \end{corollary}
% \begin{IEEEproof} Write
% \begin{align*}
% \expect (\rho_0 - \hat{\rho})^2 &= \expect \big( \rho_0(1 - G(0)) + G(0)\rho_0 - \hat{\rho} \big)^2 \\
% &= \expect \big( \rho_0(1 - G(0)) - \hat{m}_L \big)^2 \\
% &= \rho_0^2(1 - G(0))^2 + \expect \hat{m}_L^2 - 2\rho_0(1 - G(0))\expect\hat{m}_L.
% \end{align*} 
% From Theorem~\ref{thm:normality} it follows that $\expect \hat{m}_L^2 = \tfrac{B}{L} + o(L^{-1})$ and that $\expect \hat{m}_L = o(L^{-1/2})$. 
% \end{IEEEproof}

@@

For Theorem~\ref{thm:normality} the integral defining $g(\phi)$ must exist at $\phi = \tfrac{2\pi}{M}k + \frac{\pi}{M}$ for $k = 0, \dots, M-1$ in order the constant $H$ to exist.  The next proposition shows that the assumptions made in Theorem~\ref{thm:normality} are strong enough to ensure that the integral does exist at these points.  At the same time we derive some properties that will be useful during the proof of Theorem~\ref{thm:normality}.

\begin{proposition}\label{prop:gg2cont}
Let $W$ be a circularly symmetric complex random variable with $\expect\abs{W}^2$ finite.  Let $R > 0$ and $\Phi \in [0, 2\pi)$ be random variables satisfying $R e^{j\Phi} = 1 + W$.  Let $f(r,\phi)$ be the joint pdf of $R$ and $\Phi$.  Then
\[
g(\phi) = \int_{0}^\infty r f(r, \phi) dr,
\]
and
\[
g_2(\phi) = \int_{0}^\infty r^2 f(r, \phi) dr
\]
are even functions on $(-\pi,\pi)$ and are continuous at $\phi = \tfrac{2\pi}{M}k + \frac{\pi}{M}$ for $k = 0, \dots, M-1$.
\end{proposition}
\begin{IEEEproof}
BLERG
\end{IEEEproof}

A key assumption in Theorem~\ref{thm:consistency} is that $\abs{G(x)}$ is uniquely maximised at $x = 0$ for $x \in [-\pi, \pi)$.  This assumption asserts that $\abs{G(x)} \leq \abs{G(0)}$ for all $x \in [-\pi, \pi)$ and that if $\{x_i\}$ is a sequence such that $\abs{G(x_i)} \rightarrow \sabs{G(0)}$ as $i \rightarrow \infty$ then $x_i \rightarrow 0$ as $i \rightarrow \infty$.  Although we will not prove it here, this assumption is not only sufficient, but also nescessary, for if $\abs{G(x)}$ is uniquely maximised at some point $x \neq 0$ then $\sfracpart{\theta_0 - \hat{\theta}}_\pi \rightarrow x$ almost surely as $L\rightarrow\infty$, while if $\abs{G(x)}$ is not uniquely maximised then $\sfracpart{\theta_0 - \hat{\theta}}_\pi$ will not converge.  The next Lemma describes a class of circularly symmetric distributions for which $\abs{G(x)}$ is uniquely maximised at $x = 0$.  The zero mean complex Gaussian distribution with independent real and imaginary parts is apart of this class.

\begin{proposition}\label{prop:contgg2}
Let $W = X + jY$ be a circularly symmetric complex random variable with pdf $f_{X,Y}(x,y)$ of the real and imaginary parts nonincreasing with $x^2 + y^2$.  Let $R > 0$ and $\Phi \in [0, 2\pi)$ be random variables satisfying $R e^{j\Phi} = 1 + W$.  Let,
\[
h_1(x) = \expect R \cos(x + \Phi) \;\;\; \text{and} \;\;\; h_2(x) =  \expect R \cos\sfracpart{x + \Phi}.
\]
Then $\abs{h_1(x)}$ is uniquely maximised at $x=0$ over the interval $[-\pi,\pi]$ and $\abs{h_2(x)}$ is uniquely maximised at $x = 0$ over the interval $[-\tfrac{\pi}{M},\tfrac{\pi}{M}]$.
\end{proposition}
\begin{IEEEproof}
BLERG
\end{IEEEproof}

% \begin{IEEEproof}
% We only give a proof for $g_2$, the proof for $g$ begin similar.  From~\eqref{eq:pdfRPhi},
% \[
% g_2(\phi) = \int_{0}^\infty \frac{r^3 f_Z(\sqrt{\sabs{r^2 - 2r\cos\phi + 1}})}{2\pi\sqrt{\sabs{r^2 - 2r\cos\phi + 1}}} dr.
% \]
% That $g_2$ is even on $[-\pi,\pi]$ is now obvious because $\cos\phi$ is even on $[-\pi,\pi]$.  Put $a = \cos\phi$ and $z^2 = r^2 - 2ra + 1$ and by a change of variable from $r$ to $z$,
% \[
% g_2(\phi) = \int_{1}^{\sqrt{1-a^2}} \frac{r^3 f_Z(z)}{2\pi ( r - a)} dz + \int_{\sqrt{1-a^2}}^\infty \frac{r^3 f_Z(z)}{2\pi ( r - a)} dz.
% \]
% when $0 < a \leq 1$ and
% \[
% g_2(\phi) = \int_{1}^\infty \frac{r^3 f_Z(z)}{2\pi ( r - a)} dz.
% \]
% when $-1 \leq a \leq 0$.  Because
% \[
% \frac{r^3}{(r - a)} \leq a z^2 +  b
% \]
% for all $\phi \in \reals$, it follows that
% \[
% g_2(\phi) \leq \int_{0}^\infty \frac{(a z^2 + d) f_Z(z)}{2\pi} dz = a \expect Z^2 + b
% \]
% which is finite.  BLERG work out a and b.
% \end{IEEEproof}

@@

Let the noise sequence $\{w_i\}$ be complex Gaussian with independent real and imaginary parts having zero mean and variance $\sigma^2$.  The joint density function of the real and imaginary parts is then
\[
p(x,y) = \frac{1}{2\pi\sigma^2}e^{-(x^2 + y^2)/\sigma^2}
\]
Theorem~\ref{thm:consistency}~and~\ref{thm:normality} hold and, since the distribution of $w_1$ is circularly symetric, the distribution of $R_1e^{j\Phi_1}$ is identical to the distribution of $1 + \frac{1}{\rho_0} w_1$.
%and the joint density function of the real and imaginary parts of $Z$ is
%\[
%p_Z(x,y) = \rho_0^2 p( \rho_0 (x - 1), \rho_0 y ) = \frac{\kappa^2}{2\pi}e^{-\kappa^2(x ^2 - 2x + 1 + y^2) }
%\] 
%where $\kappa = \tfrac{\rho_0}{\sigma}$.  
It can be shown that
\[
g(\phi) = \frac{\cos^2(\phi)}{4\sqrt{\pi}}\left( \frac{e^{-\kappa^2} }{\sqrt{\pi}} + \kappa \Psi(\phi)  e^{-\kappa^2\sin^2(\phi)}\cos(\phi) \right)
\]
where $\kappa = \rho_0/\sigma$ and
\[
\Psi(\phi) = 1 + \erf(\kappa \cos(\phi)) = 1 + \frac{2}{\sqrt{\pi}}\int_0^{\kappa \cos(\phi)} e^{-t^2} dt .
\]
The value of $A_1, A_2, B_1$ and $B_2$ can be efficiently computed by numerical integration using these formula.
